\documentclass[11pt,a4paper]{article}
\usepackage[left=1in,right=1in]{geometry}
\usepackage{enumerate}
\title{ITU.Film bylaws (draft)}
\date{\today}
\author{General Assembly of TBA}
\newcommand{\HRule}{\noindent\rule{\linewidth}{0.5mm}}


\makeatletter
% Format the paragraphs. The command expects an argument (the number of the paragraph).
\renewcommand{\paragraph}[1]{\@startsection{paragraph}{4}{\z@}%
  {-3.25ex\@plus -1ex \@minus -.2ex}%
  {0ex}
  {\normalfont\normalsize\bfseries}{}{\bf{\S~#1.}}}
\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{\z@}%
  {-3.25ex\@plus -1ex \@minus -.2ex}%
  {0ex}
  {\normalfont\normalsize\bfseries}{}{\bf{pt.~#1.}}}

\makeatother

\begin{document}
\maketitle

\HRule
\section*{Name and address}
\paragraph{1} The name of the organisation is \emph{ITU.Film}
\subparagraph{1}The organisation is situated at the \emph{IT University of Copenhagen (ITU); Rued Langgaards Vej 7, 2300, K\o benhavn S, att: ITU.Film}
\subparagraph{2} The organisation is constituted as an Almindelige forening.

\section*{Purpose}
\paragraph{2} ITU.Film aims to be the student driven film community providing cinematic experiences to the students at the IT University of Copenhagen.

\section*{Organisational structure}
\paragraph{3} ITU.Film consist of a body, the \emph{ITU.Film crew}, of present and alumni students of ITU.
\subparagraph{1} The ITU.Film board consist of a presidium of three members of the crew elected at General assembly.
\subparagraph{2} The board has the responsibility of keeping a list of current members of the crew and to organize crew meetings.
\subparagraph{3} New members of the crew must be approved by the current board.
\subparagraph{4} Any members of crew can be excluded by a 2/3 majority crew vote.
\subparagraph{5} Only the crew has authority to exclude members.

\section*{The ITU.Film crew}
\paragraph{4} The \emph{ITU.Film crew} is responsible for the work of the organization, and has the highest ranking authority between general assemblies.
\paragraph{5} Crew meetings must be held at least two times each semester.
\subparagraph{1} The members of crew each have one vote.
\subparagraph{2} The crew elects, from its midst, people in charge of moderating, taking minutes and counting votes at each meeting.
\paragraph{6} The crew is responsible for the work program of ITU.Film.

\section*{The Board}
\paragraph{7} The Board administers the daily work of ITU.Film and acts on mandate of the general assembly and the crew
\subparagraph{1} The board shall inform the crew of all major financial, organizational or decisions of any other kind, if possible before they are taken, or at least at the next crew meeting.
\subparagraph{2} It is the boards responsibility that all cinematic events branded under ITU.Film is conducted with the appropriate rights and licenses.
\subparagraph{3} The members of the Board each have one vote. The president of ITU.Film has the deciding vote in case of split votes
\subparagraph{4} External participants can be invited to board meetings, but will not have voting rights.
\subparagraph{5} The crew can substitute any withdrawn member of the board from it's body between general assemblies.

\section*{The presidium}
\paragraph{8} The presidium consists of a President, Vice-President and Event Coordinator.
\subparagraph{1} The presidium holds the responsibility for the daily organisational, financial and legal administration.
\subparagraph{2} The presidium is responsible for convoking crew and board meetings.

\section*{General Assembly}
\paragraph{11} The General Assembly is the highest authority of ITU.Film.
\subparagraph{1} The Board must convoke a General Assembly no later than 2 weeks before the actual meeting.
\subparagraph{2} Amendments to the bylaws must be received by the Board, 1 week before the meeting at the latest.
\subparagraph{3} The budget and financial report needs to be public 2 weeks before the actual meeting. Amendments to the budget and financial report, must be received by the Board 1 week before the actual meeting.
\subparagraph{4} An ordinary General Assembly is held annually.
\subparagraph{5} The agenda for the annual General Assembly shall at least include the following items:
\begin{enumerate}
\item{Election of a chairman, secretary and two vote counters for the general assembly.}
\item{Annual report from the president.}
\item{Approval of the annual report.}
\item{Debate and vote on proposed changes for by-laws and work-program.}
\item{Presentation of the budget by the presidium.}
\item{Debate and vote on proposed changes for the budget.}
\item{Election of President, Vice-President and Event coordinator.}
\item{Any other business.}
\end{enumerate}

\paragraph{12} Proposals for the work programme, shall be received by the Board, no later than one week before the assembly.

\subparagraph{2} To run for the Board the candidates must be members of the crew at time of the general assembly.

\paragraph{13} All members of crew have one vote.

\subparagraph{1} The General Assembly makes its decisions by simple majority (one vote more than half of the valid votes) and by show of hands.

\subparagraph{2} At an election of one or more individuals written voting is applied. Also, the rule of simple majority applies.

\paragraph{14} All students at ITU have the right of speech at the general assembly. External participants can be granted a right to speak by the general assembly.

\section*{Extraordinary General Assembly}
\paragraph{15} Extraordinary General Assembly may be held whenever the crew deems it necessary, and must be held when at least 1/3 of the crew members have made a request to the President. In such cases the extraordinary general assembly must be held no later than four weeks after the request has been made.
\subparagraph{1} The deadline for convoking an extraordinary general assembly is 2 weeks.

\section*{Financials and accounting}
\paragraph{16} The organisation's fiscal year runs from 1st January to 31 December.
\subparagraph{1} The Board, under accountability to the general assembly, should strive to follow the budget.
\subparagraph{2} The crew's records are kept by the presidium.
\paragraph{17} The organisation is legally bound by the signatures of the President and at least one crew member who are not a member of the presidium.

\section*{Amendments to the by-laws}
\paragraph{18} Amendments can be amended with simple majority at a general assembly.
\subparagraph{1} \S 1, \S 2 and \S 3 can only be amended by $2/3$ majority.
\subparagraph{2} Amendments take effect after they are passed.
\subparagraph{3} Changes to proposals of amendments are permitted during the meeting, at which the proposals are discussed.

\section*{Dissolution}
\paragraph{19} Dissolution of the union can only take place with $2/3$ majority at a general assembly.
\subparagraph{1} The union's assets, in the event of dissolution, are to be used in accordance with the organisation's purposes (see \S 2) or other charitable causes. Resolution on the specific use of the property are taken by the disintegrating general assembly.
\paragraph{22} If no presidium is elected at a general assembly, a extraordinary general assembly must be held within two months. If no presidium is elected then, ITU.Film must be dissolved.
\subparagraph{1}
In the absence of a presidium, the crew acts as executive committee.

\end{document}
